MRD_final_microbiome

### 2019-06-19 GlobalMicrobiome_NS.Rmd
updated

coef <- coefficients(permanova)["mnd1",]
top.coef <- coef[rev(order(abs(coef)))[1:20]]
par(mar = c(3, 14, 2, 1))
barplot(sort(top.coef), col = rainbow(20), horiz = T, las = 1, main = "Top Genus")

ggsave("LvH.png")

@@

pseqLvM <- merge_phyloseq(p.low,p.med)

pseq.rel <- microbiome::transform(pseqLvM, "compositional")
otu <- abundances(pseq.rel)
meta <- meta(pseq.rel)

library(vegan)
permanova <- adonis(t(otu) ~ mnd,
               data = meta, permutations=999, method = "bray")

# P-value
print(as.data.frame(permanova$aov.tab)["mnd", "Pr(>F)"])

dist <- vegdist(t(otu))
anov <- anova(betadisper(dist, meta$mnd))
summary(anov)
tidy(anov)

coef <- coefficients(permanova)["mnd1",]
top.coef <- coef[rev(order(abs(coef)))[1:20]]
par(mar = c(3, 14, 2, 1))

barplot(sort(top.coef), col = rainbow(20), horiz = T, las = 1, font.axis = 3, main = "Top Genus")

ggsave("LvM.png", width = 20, height = 20, units = "cm")

@@

plot.comp.rel <- plot_composition(pseq.ph.rel, average_by = "mnd", x.label = "MND Incidence", plot.type = "barplot")

plot.comp.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("phylum_abundance_bar.png")

@@

p.new.rel <- microbiome::transform(p.new, "compositional")

plot.p.new.rel <- plot_composition(p.new.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")

plot.p.new.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("pnew_abundance_bar.png")

@@

plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")

plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("cl_abundance_bar.png")

@@

plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")

plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "A")

>>>>

# MDN
mnd.coef <- coefficients(mnd.permanova)["mnd1",]
mnd.top.coef <- coef[rev(order(abs(mnd.coef)))[1:20]]
par(mar = c(3, 14, 2, 1))
barplot(sort(mnd.top.coef), col = rainbow(20), horiz = T, las = 1, main = "Top Genus") 
ggsave("mndLvH.png")

# PD
pd.coef <- coefficients(pd.permanova)["pd1",]
pd.top.coef <- coef[rev(order(abs(pd.coef)))[1:20]]
par(mar = c(3, 14, 2, 1))
barplot(sort(pd.top.coef), col = rainbow(20), horiz = T, las = 1, main = "Top Genus") 
ggsave("pdLvH.png")

# PD
ad.coef <- coefficients(ad.permanova)["ad1",]
ad.top.coef <- coef[rev(order(abs(ad.coef)))[1:20]]
par(mar = c(3, 14, 2, 1))
barplot(sort(ad.top.coef), col = rainbow(20), horiz = T, las = 1, main = "Top Genus") 
ggsave("adLvH.png")

@@

#MND
mnd.pseqLvM <- merge_phyloseq(mnd.p.low,mnd.p.med)
mnd.pseq.rel <- microbiome::transform(mnd.pseqLvM, "compositional")
mnd.otu <- abundances(mnd.pseq.rel)
mnd.meta <- meta(mnd.pseq.rel)

#PD
pd.pseqLvM <- merge_phyloseq(pd.p.low,pd.p.med)
pd.pseq.rel <- microbiome::transform(pd.pseqLvM, "compositional")
pd.otu <- abundances(pd.pseq.rel)
pd.meta <- meta(pd.pseq.rel)

#AD
ad.pseqLvM <- merge_phyloseq(ad.p.low,ad.p.med)
ad.pseq.rel <- microbiome::transform(ad.pseqLvM, "compositional")
ad.otu <- abundances(ad.pseq.rel)
ad.meta <- meta(ad.pseq.rel)

# MND
library(vegan)
mnd.permanova <- adonis(t(mnd.otu) ~ mnd,
               data = meta, permutations=999, method = "bray")
# P-value
print(as.data.frame(mnd.permanova$aov.tab)["mnd", "Pr(>F)"])
mnd.dist <- vegdist(t(mnd.otu))
mnd.anov <- anova(betadisper(mnd.dist, mnd.meta$mnd))
summary(mnd.anov)
tidy(mnd.anov)
mnd.coef <- coefficients(mnd.permanova)["mnd1",]
mnd.top.coef <- coef[rev(order(abs(mnd.coef)))[1:20]]
par(mar = c(3, 14, 2, 1))
barplot(sort(mnd.top.coef), col = rainbow(20), horiz = T, las = 1, font.axis = 3, main = "Top Genus")
ggsave("mndLvM.png", width = 20, height = 20, units = "cm")

# PD
library(vegan)
pd.permanova <- adonis(t(pd.otu) ~ pd,
               data = meta, permutations=999, method = "bray")
# P-value
print(as.data.frame(pd.permanova$aov.tab)["pd", "Pr(>F)"])
pd.dist <- vegdist(t(pd.otu))
pd.anov <- anova(betadisper(pd.dist, pd.meta$pd))
summary(pd.anov)
tidy(pd.anov)
pd.coef <- coefficients(pd.permanova)["pd1",]
pd.top.coef <- coef[rev(order(abs(pd.coef)))[1:20]]
par(mar = c(3, 14, 2, 1))
barplot(sort(pd.top.coef), col = rainbow(20), horiz = T, las = 1, font.axis = 3, main = "Top Genus")
ggsave("pdLvM.png", width = 20, height = 20, units = "cm")

# AD
library(vegan)
ad.permanova <- adonis(t(ad.otu) ~ ad,
               data = meta, permutations=999, method = "bray")
# P-value
print(as.data.frame(ad.permanova$aov.tab)["ad", "Pr(>F)"])
ad.dist <- vegdist(t(ad.otu))
ad.anov <- anova(betadisper(ad.dist, ad.meta$ad))
summary(ad.anov)
tidy(ad.anov)
ad.coef <- coefficients(ad.permanova)["ad1",]
ad.top.coef <- coef[rev(order(abs(ad.coef)))[1:20]]
par(mar = c(3, 14, 2, 1))
barplot(sort(ad.top.coef), col = rainbow(20), horiz = T, las = 1, font.axis = 3, main = "Top Genus")
ggsave("adLvM.png", width = 20, height = 20, units = "cm")

@@

pseq.ph <- aggregate_taxa(pseq, "Phylum")
pseq.ph.rel <- microbiome::transform(pseq.ph, "compositional")
#MND
plot.comp.rel <- plot_composition(pseq.ph.rel, average_by = "mnd", x.label = "MND Incidence", plot.type = "barplot")
plot.comp.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("mndphylum_abundance_bar.png")
#PD
plot.comp.rel <- plot_composition(pseq.ph.rel, average_by = "pd", x.label = "PD Incidence", plot.type = "barplot")
plot.comp.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("pdphylum_abundance_bar.png")
#AD
plot.comp.rel <- plot_composition(pseq.ph.rel, average_by = "ad", x.label = "AD Incidence", plot.type = "barplot")
plot.comp.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("adphylum_abundance_bar.png")
```

@@

p.new.rel <- microbiome::transform(p.new, "compositional")
#MND
plot.p.new.rel <- plot_composition(p.new.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")
plot.p.new.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("mndpnew_abundance_bar.png")
#PD
plot.p.new.rel <- plot_composition(p.new.rel, average_by = "pd", x.label = "sample", plot.type = "barplot")
plot.p.new.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("pdpnew_abundance_bar.png")
#AD
plot.p.new.rel <- plot_composition(p.new.rel, average_by = "ad", x.label = "sample", plot.type = "barplot")
plot.p.new.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("adpnew_abundance_bar.png")

@@

#MND
plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("mndcl_abundance_bar.png")

#PD
plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "pd", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("pdcl_abundance_bar.png")

#AD
plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "ad", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "plasma") 
ggsave("adcl_abundance_bar.png")

@@

plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "A")
